### 2025-06-20 manuscripts/09-JERP-v2/manuscript_main.tex
edit synthetic parents

I use the 1994–2019 CPS data set to study the effect of Hispanic surnames on labor market outcomes, because that span contains data on parents’ place of birth, ethnicity, and race. The CPS does not provide data on parents’ characteristics, essential to determine the family background, but the 1960–2000 US Census data includes parents’ place of birth, race, and ethnicity. I employ this information to construct "synthetic parents" using a method developed by \textcite{rubinstein2014pride} linking husbands and wives  in the census data. Assuming that parents have children 25–40 years old, I link these “parents” using parents’ places of birth, birth year of "children," and the parents’ places of birth.

>>>>

I use the 1994–2019 CPS data set to study the effect of Hispanic surnames on labor market outcomes, because that span contains data on parents’ place of birth, ethnicity, and race. The CPS does not provide data on parents’ characteristics, essential to determine the family background, but the 1960–2000 US Census data includes parents’ place of birth, race, and ethnicity. I employ this information to construct ``synthetic parents'' using a method developed by \textcite{rubinstein2014pride} linking husbands and wives  in the census data. Assuming that parents have children 25–40 years old, I link these “parents” using parents’ places of birth, birth year of ``children,'' and the parents’ places of birth.

### 2025-06-20 manuscripts/10-JERP-v3/manuscript_main.tex
edit synthetic parents

This aggregation process introduces some heterogeneity, as individual parents vary considerably from these group-level measures. However, this approach provides valuable information about typical family background characteristics that would otherwise be completely unobserved \autocite{rubinstein2014pride,aaronson2008intergenerational}. The synthetic parents' characteristics serve as useful proxies for the socioeconomic environment in which these children were raised, allowing me to control for important background factors that influence educational and labor market outcomes. While more refined matching would be ideal, the publicly available data limit the potential matching dimensions. Nevertheless, the current approach provides meaningful estimates while acknowledging these data constraints.

@@

\textbf{Labor market outcomes}:
\begin{itemize}
\item Unemployment (binary indicator from civilian labor force status)
\item Log annual earnings (from ASEC supplement)
\item Log weekly earnings (from outgoing rotation for hourly workers)
\end{itemize}
\textbf{Controls}: Age, hours worked, state-year fixed effects, and synthetic parents' characteristics (income and education) in alternative specifications.

>>>>

Importantly, these synthetic parent measures are constructed to show that interethnic couples are more comparable to each other in terms of observable characteristics, thereby reducing potential bias in comparisons. The synthetic parent variables are used exclusively for descriptive summary statistics and are not included as control variables in the main regression analyses.

This aggregation process introduces some heterogeneity, as individual parents vary considerably from these group-level measures. However, this approach provides valuable information on typical characteristics of family history that would otherwise be completely unobserved \autocite{rubinstein2014pride,aaronson2008intergenerational}. The synthetic parents' characteristics serve as useful proxies for the socioeconomic environment in which these children were raised, allowing me to control for important background factors that influence educational and labor market outcomes. While the synthetic parents' characteristics provide useful information about the socioeconomic environment in which these children were raised, they are not used as control variables in the regression analyses. More refined matching would be ideal, the publicly available data limit the potential matching dimensions. Nevertheless, the current approach provides meaningful information from the data on the different type of couples, i.e. interethnic versus endogamous.

@@

\textbf{Labor market outcomes}:
\begin{itemize}
\item Unemployment (binary indicator from civilian labor force status)
\item Log annual earnings (from ASEC supplement)
\item Log weekly earnings (from outgoing rotation for hourly workers)
\end{itemize}
\textbf{Controls}: Age, hours worked, and state-year fixed effects.

### 2025-06-20 manuscripts/10-JERP-v3/submit_journal-main.tex
edit synthetic parents

        I acknowledge the reviewer's suggestion about including additional characteristics to improve the matching quality. While incorporating more matching variables (such as parent's age at birth) could potentially reduce heterogeneity within the synthetic parent groups, the current approach balances precision with sample size considerations. Adding more matching criteria would create increasingly small cells in the Census data, potentially leading to unstable estimates or empty cells, particularly for less common parent birthplace combinations. Moreover, since the synthetic parent characteristics serve as controls rather than the primary variables of interest, the current level of aggregation is sufficient for the paper's main empirical strategy. 
\end{spacing}

\begin{spacing}{\rrxspc}
    I also acknowledge the limitations: ``This aggregation process introduces some heterogeneity, as individual parents vary considerably from these group-level measures. However, this approach provides valuable information about typical family background characteristics that would otherwise be completely unobserved. The synthetic parents' characteristics serve as useful proxies for the socioeconomic environment in which these children were raised, allowing me to control for important background factors that influence educational and labor market outcomes. While more refined matching would be ideal, the publicly available data limit the potential matching dimensions. Nevertheless, the current approach provides meaningful estimates while acknowledging these data constraints.''
\end{spacing}

@@

\begin{spacing}{\rrxspc}
    I am grateful to the referee for raising this important concern. I have expanded the discussion of these methodological issues in the empirical approach section. Regarding the generated regressor issue, I updated the regression results in the manuscript with results that do not include the specification where  `synthetic parents` are included in the controls. This alleviates the concern regarding generated, as they are no longer in the regression.

>>>>

        I acknowledge the reviewer's suggestion about including additional characteristics to improve the matching quality. While incorporating more matching variables (such as parent's age at birth) could potentially reduce heterogeneity within the synthetic parent groups, the current approach balances precision with sample size considerations. Adding more matching criteria would create increasingly small cells in the Census data, potentially leading to unstable estimates or empty cells, particularly for less common parent birthplace combinations. Moreover, since the synthetic parent characteristics are used exclusively for descriptive summary statistics and not as control variables in the main regression analyses, the current level of aggregation is appropriate for the paper's empirical strategy.
\end{spacing}

@@

\begin{spacing}{\rrxspc}
    I am grateful to the referee for raising this important concern. I have expanded the discussion of these methodological issues in the empirical approach section. Regarding the generated regressor issue, I updated the regression results in the manuscript with results that do not include the specification where  `synthetic parents` are included in the controls. This alleviates the concern regarding generated, as they are no longer in the regression. I also updated the manuscript to make sure that it is clear that `synthetic parents` parents are only used for descriptive summary statistics to enhance comparability between interethnic families and are not included as control variables in any of the main regressions.
